---
title: "A Look Back at PEL Phase 2"
author: "u/firstoverall"
date: 2019-07-10
categories: ["PEL", "PUBG"]
tags: ["PEL", "PUBG", "Phase 2"]
---

```{r setup, include = FALSE}

knitr::opts_chunk$set(collapse = TRUE)
library(here)
library(knitr)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(ggrepel)
library(ggthemes)
library(viridis)
library(magrittr)
library(tibble)
library(plotly)
library(transformr)
library(units)
library(vegan)
diversity_boot <- here("static", "CERE.RData") 
load(diversity_boot)

Sys.setenv("plotly_username" = "descent")
Sys.setenv("plotly_api_key" = "KOJaKam6unaHMsBRocxh")
Sys.setenv(TZ = "MST")

# below you will find the gory R code of a biologist; proceed with caution

```

```{r pel_points, include = FALSE}

# create the dataframe
# match 1 data
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_1
PEL_1 <- tibble(placement_points = c(10, 1, 6, 3,
                                     4, 0, 0, 2,
                                     5, 0, 1, 0,
                                     0, 0, 0, 0),
                kill_points = c(9, 7, 6, 3, 
                                4, 0, 3, 2, 
                                10, 1, 6, 4, 
                                1, 3, 0, 0),
                team = c("G2", "NV", "PK", "FC", 
                         "EZ4", "TL", "WIN", "DA",
                         "CC", "NIP", "RYE", "VIT",
                         "TSM", "UT", "REC", "M19"),
                match = 1)

PEL_data <- PEL_1

# match 2
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_1
PEL_2 <- tibble(placement_points = c(1, 0, 3, 4,
                                     0, 10, 6, 5,
                                     0, 1, 2, 0,
                                     0, 0, 0, 0),
                kill_points = c(10, 0, 6, 3, 
                                2, 10, 5, 5, 
                                3, 5, 4, 2, 
                                1, 1, 0, 2),
                team = c("G2", "NV", "PK", "FC", 
                         "EZ4", "TL", "WIN", "DA",
                         "CC", "NIP", "RYE", "VIT",
                         "TSM", "UT", "REC", "M19"),
                match = 2)
PEL_data <- bind_rows(PEL_data, PEL_2)

# match 3
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_1
PEL_3 <- tibble(placement_points = c(5, 3, 1, 10,
                                     0, 1, 0, 6,
                                     0, 0, 0, 0,
                                     2, 4, 0, 0),
                kill_points = c(0, 8, 5, 9,
                                2, 4, 0, 3,
                                1, 5, 4, 6,
                                7, 1, 2, 2),
                team = c("G2", "NV", "PK", "FC", 
                         "EZ4", "TL", "WIN", "DA",
                         "CC", "NIP", "RYE", "VIT",
                         "TSM", "UT", "REC", "M19"),
                match = 3)
PEL_data <- bind_rows(PEL_data, PEL_3)

# match 4
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_1
PEL_4 <- tibble(placement_points = c(3, 10, 4, 0,
                                     6, 0, 5, 0,
                                     0, 2, 0, 0,
                                     1, 0, 0, 1),
                kill_points = c(5, 10, 7, 0,
                                13, 3, 4, 0,
                                1, 5, 1, 3,
                                1, 1, 5, 2),
                team = c("G2", "NV", "PK", "FC", 
                         "EZ4", "TL", "WIN", "DA",
                         "CC", "NIP", "RYE", "VIT",
                         "TSM", "UT", "REC", "M19"),
                match = 4)
PEL_data <- bind_rows(PEL_data, PEL_4)

# match 5
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_1
PEL_5 <- tibble(placement_points = c(0, 4, 6, 0,
                                     5, 1, 10, 0,
                                     0, 3, 1, 0,
                                     0, 2, 0, 0),
                kill_points = c(7, 7, 7, 1, 
                                4, 3, 6, 2, 
                                2, 5, 3, 2, 
                                0, 3, 4, 5),
                team = c("DA", "G2", "TSM", "NV", 
                         "FC", "RYE", "M19", "VIT",
                         "TL", "NIP", "EZ4", "WIN",
                         "PK", "CC", "REC", "UT"),
                match = 5)
PEL_data <- bind_rows(PEL_data, PEL_5)

# match 6
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_1
PEL_6 <- tibble(placement_points = c(4, 0, 5, 1, 
                                     1, 10, 0, 0, 
                                     0, 6, 0, 0, 
                                     2, 0, 3, 0),
                kill_points = c(2, 2, 5, 7, 
                                5, 9, 3, 3, 
                                2, 7, 6, 0, 
                                5, 3, 0, 0),
                team = c("DA", "G2", "TSM", "NV", 
                         "FC", "RYE", "M19", "VIT",
                         "TL", "NIP", "EZ4", "WIN",
                         "PK", "CC", "REC", "UT"),
                match = 6)
PEL_data <- bind_rows(PEL_data, PEL_6)

# match 7
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_1
PEL_7 <- tibble(placement_points = c(3, 0, 2, 10, 
                                     5, 0, 1, 0, 
                                     6, 1, 0, 4, 
                                     0, 0, 0, 0),
                kill_points = c(4, 7, 10, 10, 
                                4, 4, 2, 6, 
                                8, 0, 1, 4, 
                                0, 0, 1, 0),
                team = c("DA", "G2", "TSM", "NV", 
                         "FC", "RYE", "M19", "VIT",
                         "TL", "NIP", "EZ4", "WIN",
                         "PK", "CC", "REC", "UT"),
                match = 7)
PEL_data <- bind_rows(PEL_data, PEL_7)

# match 8
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_1
PEL_8 <- tibble(placement_points = c(10, 4, 0, 0, 
                                     1, 0, 0, 6, 
                                     2, 0, 5, 0, 
                                     3, 1, 0, 0),
                kill_points = c(11, 13, 1, 4, 
                                3, 0, 3, 7, 
                                3, 0, 1, 4, 
                                2, 1, 1, 1),
                team = c("DA", "G2", "TSM", "NV", 
                         "FC", "RYE", "M19", "VIT",
                         "TL", "NIP", "EZ4", "WIN",
                         "PK", "CC", "REC", "UT"),
                match = 8)
PEL_data <- bind_rows(PEL_data, PEL_8)

# match 9
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_1
PEL_9 <- tibble(placement_points = c(3, 10, 5, 0, 
                                     0, 0, 0, 6, 
                                     0, 0, 2, 4, 
                                     1, 1, 0, 0),
                kill_points = c(9, 11, 8, 2, 
                                4, 1, 6, 5, 
                                0, 2, 1, 1, 
                                1, 4, 1, 1),
                team = c("TSM", "WIN", "CC", "FC",
                         "G2", "DA", "NV", "TL",
                         "NIP", "VIT", "EZ4", "M19",
                         "UT", "PK", "REC", "RYE"),
                match = 9)
PEL_data <- bind_rows(PEL_data, PEL_9)

# match 10
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_1
PEL_10 <- tibble(placement_points = c(3, 6, 1, 0, 
                                      0, 4, 5, 0, 
                                      10, 0, 2, 0, 
                                      0, 0, 1, 0),
                 kill_points = c(7, 6, 2, 1, 
                                 5, 2, 7, 5, 
                                 5, 0, 5, 4, 
                                 3, 5, 0, 1),
                 team = c("TSM", "WIN", "CC", "FC",
                          "G2", "DA", "NV", "TL",
                          "NIP", "VIT", "EZ4", "M19",
                          "UT", "PK", "REC", "RYE"),
                 match = 10)
PEL_data <- bind_rows(PEL_data, PEL_10)

# match 11
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_1
PEL_11 <- tibble(placement_points = c(1, 0, 0, 10, 
                                      0, 0, 3, 0, 
                                      0, 6, 5, 1, 
                                      4, 0, 2, 0),
                 kill_points = c(1, 2, 8, 16, 
                                 6, 2, 3, 0, 
                                 0, 7, 0, 3, 
                                 4, 0, 1, 0),
                 team = c("TSM", "WIN", "CC", "FC",
                          "G2", "DA", "NV", "TL",
                          "NIP", "VIT", "EZ4", "M19",
                          "UT", "PK", "REC", "RYE"),
                 match = 11)
PEL_data <- bind_rows(PEL_data, PEL_11)

# match 12
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_1
PEL_12 <- tibble(placement_points = c(5, 2, 1, 0, 
                                      6, 10, 0, 4,
                                      3, 1, 0, 0, 
                                      0, 0, 0, 0),
                 kill_points = c(9, 0, 8, 0, 
                                 7, 9, 2, 5, 
                                 5, 3, 1, 2, 
                                 1, 3, 0, 2),
                 team = c("TSM", "WIN", "CC", "FC",
                          "G2", "DA", "NV", "TL",
                          "NIP", "VIT", "EZ4", "M19",
                          "UT", "PK", "REC", "RYE"),
                 match = 12)
PEL_data <- bind_rows(PEL_data, PEL_12)

# match 13
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_2
PEL_13 <- tibble(placement_points = c(0, 10, 1, 6,
                                      2, 5, 0, 4,
                                      0, 3, 0, 0,
                                      0, 0, 1, 0),
                 kill_points = c(3, 11, 4, 8,
                                 7, 9, 1, 2,
                                 2, 4, 3, 1,
                                 3, 1, 1, 1),
                 team = c("FC", "NV", "NIP", "WIN",
                          "TSM", "G2", "TL", "RYE",
                          "EZ4", "CC", "REC", "M19",
                          "UT", "PK", "VIT", "DA"),
                 match = 13)
PEL_data <- bind_rows(PEL_data, PEL_13)

# match 14
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_2
PEL_14 <- tibble(placement_points = c(0, 10, 4, 1,
                                      6, 0, 0, 3,
                                      5, 2, 1, 0,
                                      0, 0, 0, 0),
                 kill_points = c(3, 7, 5, 2,
                                 8, 2, 6, 3,
                                 5, 1, 4, 3,
                                 6, 2, 0, 0),
                 team = c("FC", "NV", "NIP", "WIN", 
                          "TSM", "G2", "TL", "RYE",
                          "EZ4", "CC", "REC", "M19",
                          "UT", "PK", "VIT", "DA"),
                 match = 14)
PEL_data <- bind_rows(PEL_data, PEL_14)

# match 15
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_2
PEL_15 <- tibble(placement_points = c(10, 0, 0, 4,
                                      0, 0, 1, 5,
                                      3, 0, 0, 6,
                                      0, 1, 0, 2),
                 kill_points = c(13, 4, 2, 3,
                                 1, 1, 7, 4,
                                 6, 1, 0, 3,
                                 1, 3, 6, 2),
                 team = c("FC", "NV", "NIP", "WIN", 
                          "TSM", "G2", "TL", "RYE",
                          "EZ4", "CC", "REC", "M19",
                          "UT", "PK", "VIT", "DA"),
                 match = 15)
PEL_data <- bind_rows(PEL_data, PEL_15)

# match 16
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_2
PEL_16 <- tibble(placement_points = c(10, 0, 6, 0,
                                      0, 5, 3, 1,
                                      0, 0, 4, 0,
                                      2, 1, 0, 0),
                 kill_points = c(10, 2, 7, 5,
                                 4, 6, 6, 2,
                                 2, 4, 3, 2,
                                 0, 3, 1, 1),
                 team = c("FC", "NV", "NIP", "WIN", 
                          "TSM", "G2", "TL", "RYE",
                          "EZ4", "CC", "REC", "M19",
                          "UT", "PK", "VIT", "DA"),
                 match = 16)
PEL_data <- bind_rows(PEL_data, PEL_16)

# match 17
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_2
PEL_17 <- tibble(placement_points = c(10, 6, 0, 0, 
                                      4, 5, 0, 0, 
                                      2, 0, 1, 0, 
                                      1, 0, 3, 0),
                 kill_points = c(9, 16, 2, 3, 
                                 2, 4, 1, 1, 
                                 3, 2, 3, 4, 
                                 3, 0, 3, 2),
                 team = c("TL", "CC", "FC", "NV", 
                          "UT", "TSM", "PK", "REC",
                          "EZ4", "VIT", "M19", "G2",
                          "DA", "NIP", "WIN", "RYE"),
                 match = 17)
PEL_data <- bind_rows(PEL_data, PEL_17)

# match 18
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_2
PEL_18 <- tibble(placement_points = c(0, 0, 6, 10, 
                                      0, 0, 2, 5, 
                                      0, 0, 3, 0, 
                                      1, 4, 1, 0),
                 kill_points = c(1, 3, 11, 10, 
                                 2, 0, 4, 9, 
                                 1, 5, 5, 3, 
                                 2, 1, 0, 2),
                 team = c("TL", "CC", "FC", "NV", 
                          "UT", "TSM", "PK", "REC",
                          "EZ4", "VIT", "M19", "G2",
                          "DA", "NIP", "WIN", "RYE"),
                 match = 18)
PEL_data <- bind_rows(PEL_data, PEL_18)

# match 19
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_2
PEL_19 <- tibble(placement_points = c(10, 0, 0, 0, 
                                      0, 4, 3, 2, 
                                      6, 0, 0, 0, 
                                      5, 1, 0, 1),
                 kill_points = c(10, 1, 1, 2, 
                                 0, 3, 8, 4, 
                                 3, 2, 2, 6, 
                                 3, 3, 3, 1),
                 team = c("TL", "CC", "FC", "NV", 
                          "UT", "TSM", "PK", "REC",
                          "EZ4", "VIT", "M19", "G2",
                          "DA", "NIP", "WIN", "RYE"),
                 match = 19)
PEL_data <- bind_rows(PEL_data, PEL_19)

# match 20
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_2
PEL_20 <- tibble(placement_points = c(4, 5, 6, 0, 
                                      10, 3, 0, 1, 
                                      2, 1, 0, 0, 
                                      0, 0, 0, 0),
                 kill_points = c(6, 7, 6, 3, 
                                 7, 4, 4, 0, 
                                 3, 8, 3, 3, 
                                 1, 4, 1, 1),
                 team = c("TL", "CC", "FC", "NV", 
                          "UT", "TSM", "PK", "REC",
                          "EZ4", "VIT", "M19", "G2",
                          "DA", "NIP", "WIN", "RYE"),
                 match = 20)
PEL_data <- bind_rows(PEL_data, PEL_20)

# match 21
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_2
PEL_21 <- tibble(placement_points = c(2, 5, 10, 0, 
                                      4, 6, 0, 0, 
                                      3, 0, 0, 0, 
                                      1, 1, 0, 0),
                 kill_points = c(6, 8, 7, 4, 
                                 5, 0, 5, 7, 
                                 4, 1, 1, 1, 
                                 5, 0, 0, 2),
                 team = c("FC", "RYE", "M19", "G2", 
                          "DA", "TL", "TSM", "CC",
                          "NIP", "EZ4", "VIT", "REC",
                          "PK", "NV", "WIN", "UT"),
                 match = 21)
PEL_data <- bind_rows(PEL_data, PEL_21)

# match 22
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_2
PEL_22 <- tibble(placement_points = c(10, 5, 3, 2, 
                                      0, 1, 6, 0, 
                                      0, 0, 4, 1, 
                                      0, 0, 0, 0),
                 kill_points = c(8, 9, 8, 1, 
                                 1, 3, 6, 5, 
                                 11, 4, 1, 2, 
                                 0, 0, 0, 1),
                 team = c("FC", "RYE", "M19", "G2", 
                          "DA", "TL", "TSM", "CC",
                          "NIP", "EZ4", "VIT", "REC",
                          "PK", "NV", "WIN", "UT"),
                 match = 22)
PEL_data <- bind_rows(PEL_data, PEL_22)

# match 23
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_2
PEL_23 <- tibble(placement_points = c(10, 1, 0, 6, 
                                      5, 0, 4, 0, 
                                      1, 0, 0, 3, 
                                      0, 2, 0, 0),
                 kill_points = c(10, 6, 2, 10, 
                                 7, 1, 2, 5, 
                                 2, 2, 4, 2, 
                                 5, 1, 1, 0),
                 team = c("FC", "RYE", "M19", "G2", 
                          "DA", "TL", "TSM", "CC",
                          "NIP", "EZ4", "VIT", "REC",
                          "PK", "NV", "WIN", "UT"),
                 match = 23)
PEL_data <- bind_rows(PEL_data, PEL_23)

# match 24
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_2
PEL_24 <- tibble(placement_points = c(0, 1, 2, 0, 
                                      1, 10, 0, 6, 
                                      0, 5, 4, 3, 
                                      0, 0, 0, 0),
                 kill_points = c(6, 7, 0, 6, 
                                 6, 7, 2, 1, 
                                 2, 7, 5, 1, 
                                 1, 3, 4, 0),
                 team = c("FC", "RYE", "M19", "G2", 
                          "DA", "TL", "TSM", "CC",
                          "NIP", "EZ4", "VIT", "REC",
                          "PK", "NV", "WIN", "UT"),
                 match = 24)
PEL_data <- bind_rows(PEL_data, PEL_24)

# match 25
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_3
PEL_25 <- tibble(placement_points = c(5, 1, 0, 3,
                                      10, 4, 2, 0,
                                      0, 1, 0, 0,
                                      0, 0, 6, 0),
                 kill_points = c(10, 2, 3, 2,
                                 11, 9, 7, 1,
                                 3, 1, 1, 1,
                                 3, 0, 5, 1),
                 team = c("UT", "TSM", "TL", "RYE", 
                          "M19", "FC", "G2", "VIT",
                          "WIN", "PK", "NIP", "EZ4",
                          "REC", "NV", "DA", "CC"),
                 match = 25)
PEL_data <- bind_rows(PEL_data, PEL_25)

# match 26
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_3
PEL_26 <- tibble(placement_points = c(1, 6, 10, 2,
                                      4, 1, 0, 3,
                                      0, 0, 0, 0,
                                      0, 0, 0, 5),
                 kill_points = c(5, 8, 11, 3,
                                 2, 2, 0, 9,
                                 4, 6, 1, 3,
                                 2, 2, 0, 2),
                 team = c("UT", "TSM", "TL", "RYE", 
                          "M19", "FC", "G2", "VIT",
                          "WIN", "PK", "NIP", "EZ4",
                          "REC", "NV", "DA", "CC"),
                 match = 26)
PEL_data <- bind_rows(PEL_data, PEL_26)

# match 27
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_3
PEL_27 <- tibble(placement_points = c(1, 6, 10, 2,
                                      4, 1, 0, 3,
                                      0, 0, 0, 0,
                                      0, 0, 0, 5),
                 kill_points = c(5, 8, 11, 3,
                                 2, 2, 0, 9,
                                 4, 6, 1, 3,
                                 2, 2, 0, 2),
                 team = c("UT", "TSM", "TL", "RYE", 
                          "M19", "FC", "G2", "VIT",
                          "WIN", "PK", "NIP", "EZ4",
                          "REC", "NV", "DA", "CC"),
                 match = 27)
PEL_data <- bind_rows(PEL_data, PEL_27)

# match 28
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_3
PEL_28 <- tibble(placement_points = c(1, 10, 3, 0, 
                                      0, 1, 0, 0, 
                                      6, 2, 4, 5, 
                                      0, 0, 0, 0),
                 kill_points = c(8, 6, 7, 3, 
                                 1, 5, 1, 3, 
                                 6, 7, 6, 5, 
                                 2, 2, 0, 0),
                 team = c("UT", "TSM", "TL", "RYE", 
                          "M19", "FC", "G2", "VIT",
                          "WIN", "PK", "NIP", "EZ4",
                          "REC", "NV", "DA", "CC"),
                 match = 28)
PEL_data <- bind_rows(PEL_data, PEL_28)

# match 29
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_3
PEL_29 <- tibble(placement_points = c(6, 0, 10, 5, 
                                      0, 0, 4, 2, 
                                      0, 0, 3, 0, 
                                      0, 0, 1, 1),
                 kill_points = c(14, 3, 9, 5, 
                                 1, 0, 5, 5, 
                                 6, 4, 2, 1, 
                                 1, 3, 3, 1),
                 team = c("NV", "NIP", "G2", "TL", 
                          "WIN", "REC", "TSM", "CC",
                          "EZ4", "RYE", "M19", "FC",
                          "VIT", "PK", "DA", "UT"),
                 match = 29)
PEL_data <- bind_rows(PEL_data, PEL_29)

# match 30
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_3
PEL_30 <- tibble(placement_points = c(10, 6, 0, 0, 
                                      5, 4, 1, 0, 
                                      2, 3, 0, 0, 
                                      1, 0, 0, 0),
                 kill_points = c(9, 5, 3, 0, 
                                 7, 9, 7, 6, 
                                 4, 1, 1, 4, 
                                 0, 2, 2, 0),
                 team = c("NV", "NIP", "G2", "TL", 
                          "WIN", "REC", "TSM", "CC",
                          "EZ4", "RYE", "M19", "FC",
                          "VIT", "PK", "DA", "UT"),
                 match = 30)
PEL_data <- bind_rows(PEL_data, PEL_30)

# match 31
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_3
PEL_31 <- tibble(placement_points = c(5, 10, 1, 4,
                                      6, 0, 0, 2, 
                                      0, 3, 0, 0, 
                                      0, 0, 0, 1),
                 kill_points = c(3, 8, 3, 11, 
                                 11, 4, 0, 2, 
                                 2, 2, 6, 4, 
                                 2, 1, 0, 0),
                 team = c("NV", "NIP", "G2", "TL", 
                          "WIN", "REC", "TSM", "CC",
                          "EZ4", "RYE", "M19", "FC",
                          "VIT", "PK", "DA", "UT"),
                 match = 31)
PEL_data <- bind_rows(PEL_data, PEL_31)

# match 32
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_3
PEL_32 <- tibble(placement_points = c(3, 6, 10, 5, 
                                      0, 4, 2, 0, 
                                      1, 0, 0, 0, 
                                      0, 0, 0, 1),
                 kill_points = c(5, 8, 9, 5, 
                                 3, 9, 4, 2, 
                                 3, 2, 0, 1, 
                                 4, 1, 1, 2),
                 team = c("NV", "NIP", "G2", "TL", 
                          "WIN", "REC", "TSM", "CC",
                          "EZ4", "RYE", "M19", "FC",
                          "VIT", "PK", "DA", "UT"),
                 match = 32)
PEL_data <- bind_rows(PEL_data, PEL_32)

# match 33
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_3
PEL_33 <- tibble(placement_points = c(0, 10, 5, 1, 
                                      6, 0, 0, 3, 
                                      0, 0, 4, 0, 
                                      2, 0, 0, 1),
                 kill_points = c(1, 9, 5, 1, 
                                 9, 3, 4, 5, 
                                 0, 2, 3, 5, 
                                 6, 2, 2, 2),
                 team = c("NV", "EZ4", "G2", "FC", 
                          "DA", "TSM", "RYE", "PK",
                          "REC", "CC", "NIP", "TL",
                          "VIT", "UT", "M19", "WIN"),
                 match = 33)
PEL_data <- bind_rows(PEL_data, PEL_33)

# match 34
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_3
PEL_34 <- tibble(placement_points = c(0, 0, 2, 4, 
                                      0, 3, 6, 0, 
                                      10, 5, 0, 0, 
                                      0, 1, 1, 0),
                 kill_points = c(0, 0, 6, 5, 
                                 2, 1, 5, 1, 
                                 12, 11, 1, 4, 
                                 3, 2, 2, 3),
                 team = c("NV", "EZ4", "G2", "FC", 
                          "DA", "TSM", "RYE", "PK",
                          "REC", "CC", "NIP", "TL",
                          "VIT", "UT", "M19", "WIN"),
                 match = 34)
PEL_data <- bind_rows(PEL_data, PEL_34)

# match 35
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_3
PEL_35 <- tibble(placement_points = c(10, 3, 6, 5, 
                                      0, 4, 0, 1, 
                                      0, 2, 0, 0, 
                                      0, 0, 0, 1),
                 kill_points = c(7, 2, 10, 11, 
                                 5, 5, 4, 3, 
                                 2, 3, 0, 1, 
                                 2, 3, 0, 1),
                 team = c("NV", "EZ4", "G2", "FC", 
                          "DA", "TSM", "RYE", "PK",
                          "REC", "CC", "NIP", "TL",
                          "VIT", "UT", "M19", "WIN"),
                 match = 35)
PEL_data <- bind_rows(PEL_data, PEL_35)

# match 36
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_3
PEL_36 <- tibble(placement_points = c(10, 5, 0, 0, 
                                      1, 3, 2, 6, 
                                      0, 0, 4, 0, 
                                      0, 0, 1, 0),
                 kill_points = c(11, 9, 0, 4, 
                                 5, 7, 4, 5, 
                                 0, 0, 9, 4, 
                                 1, 0, 2, 0),
                 team = c("NV", "EZ4", "G2", "FC", 
                          "DA", "TSM", "RYE", "PK",
                          "REC", "CC", "NIP", "TL",
                          "VIT", "UT", "M19", "WIN"),
                 match = 36)
PEL_data <- bind_rows(PEL_data, PEL_36)

# match 37
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_4
PEL_37 <- tibble(placement_points = c(10, 3, 1, 2, 
                                      4, 6, 0, 1, 
                                      5, 0, 0, 0, 
                                      0, 0, 0, 0),
                 kill_points = c(14, 8, 4, 7, 
                                 8, 3, 2, 3, 
                                 4, 2, 0, 2, 
                                 2, 0, 0, 0),
                 team = c("PK", "FC", "VIT", "TL", 
                          "NV", "UT", "RYE", "CC",
                          "DA", "M19", "TSM", "NIP",
                          "EZ4", "REC", "WIN", "G2"),
                 match = 37)
PEL_data <- bind_rows(PEL_data, PEL_37)

# match 38
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_4
PEL_38 <- tibble(placement_points = c(0, 6, 0, 10, 
                                      1, 3, 0, 5, 
                                      0, 2, 4, 0, 
                                      0, 0, 0, 1),
                 kill_points = c(8, 5, 0, 6, 
                                 5, 2, 6, 2, 
                                 3, 3, 6, 1, 
                                 0, 0, 7, 5),
                 team = c("PK", "FC", "VIT", "TL", 
                          "NV", "UT", "RYE", "CC",
                          "DA", "M19", "TSM", "NIP",
                          "EZ4", "REC", "WIN", "G2"),
                 match = 38)
PEL_data <- bind_rows(PEL_data, PEL_38)

# match 39
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_4
PEL_39 <- tibble(placement_points = c(0, 10, 1, 0, 
                                      2, 5, 6, 1, 
                                      0, 0, 0, 4, 
                                      0, 3, 0, 0),
                 kill_points = c(1, 14, 1, 4, 
                                 3, 2, 4, 4, 
                                 3, 5, 0, 8, 
                                 0, 5, 2, 2),
                 team = c("PK", "FC", "VIT", "TL", 
                          "NV", "UT", "RYE", "CC",
                          "DA", "M19", "TSM", "NIP",
                          "EZ4", "REC", "WIN", "G2"),
                 match = 39)
PEL_data <- bind_rows(PEL_data, PEL_39)

# match 40
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_4
PEL_40 <- tibble(placement_points = c(5, 0, 10, 0, 
                                      0, 1, 1, 4, 
                                      0, 3, 6, 0, 
                                      2, 0, 0, 0),
                 kill_points = c(10, 0, 15, 1, 
                                 5, 6, 6, 2, 
                                 3, 2, 0, 0, 
                                 7, 2, 0, 1),
                 team = c("PK", "FC", "VIT", "TL", 
                          "NV", "UT", "RYE", "CC",
                          "DA", "M19", "TSM", "NIP",
                          "EZ4", "REC", "WIN", "G2"),
                 match = 40)
PEL_data <- bind_rows(PEL_data, PEL_40)

# match 41
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_4
PEL_41 <- tibble(placement_points = c(10, 3, 2, 0, 
                                      6, 1, 4, 1, 
                                      5, 0, 0, 0, 
                                      0, 0, 0, 0),
                 kill_points = c(11, 4, 5, 5, 
                                 5, 0, 9, 2, 
                                 8, 3, 0, 1, 
                                 4, 0, 3, 0),
                 team = c("NV", "RYE", "G2", "DA", 
                          "FC", "REC", "UT", "WIN",
                          "VIT", "TL", "CC", "NIP",
                          "EZ4", "M19", "TSM", "PK"),
                 match = 41)
PEL_data <- bind_rows(PEL_data, PEL_41)

# match 42
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_4
PEL_42 <- tibble(placement_points = c(0, 10, 0, 6, 
                                      0, 1, 0, 0, 
                                      4, 3, 5, 0, 
                                      1, 2, 0, 0),
                 kill_points = c(3, 12, 3, 5, 
                                 2, 1, 6, 1, 
                                 5, 8, 9, 0, 
                                 1, 0, 2, 1),
                 team = c("NV", "RYE", "G2", "DA", 
                          "FC", "REC", "UT", "WIN",
                          "VIT", "TL", "CC", "NIP",
                          "EZ4", "M19", "TSM", "PK"),
                 match = 42)
PEL_data <- bind_rows(PEL_data, PEL_42)

# match 43
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_4
PEL_43 <- tibble(placement_points = c(2, 6, 0, 0, 
                                      0, 10, 0, 4,
                                      0, 1, 1, 5, 
                                      3, 0, 0, 0),
                 kill_points = c(13, 4, 1, 3, 
                                 1, 9, 1, 8, 
                                 1, 5, 1, 4, 
                                 3, 2, 0, 1),
                 team = c("NV", "RYE", "G2", "DA", 
                          "FC", "REC", "UT", "WIN",
                          "VIT", "TL", "CC", "NIP",
                          "EZ4", "M19", "TSM", "PK"),
                 match = 43)
PEL_data <- bind_rows(PEL_data, PEL_43)

# match 44
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_4
PEL_44 <- tibble(placement_points = c(10, 1, 5, 2, 
                                      6, 0, 0, 1, 
                                      0, 0, 0, 3, 
                                      0, 4, 0, 0),
                 kill_points = c(8, 2, 16, 7, 
                                 5, 2, 3, 6, 
                                 0, 1, 2, 3, 
                                 1, 2, 0, 0),
                 team = c("NV", "RYE", "G2", "DA", 
                          "FC", "REC", "UT", "WIN",
                          "VIT", "TL", "CC", "NIP",
                          "EZ4", "M19", "TSM", "PK"),
                 match = 44)
PEL_data <- bind_rows(PEL_data, PEL_44)

# match 45
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_4
PEL_45 <- tibble(placement_points = c(0, 6, 10, 2, 
                                      0, 0, 0, 3, 
                                      4, 1, 0, 0, 
                                      5, 0, 1, 0),
                 kill_points = c(1, 7, 11, 5, 
                                 1, 0, 4, 5, 
                                 4, 2, 4, 4, 
                                 4, 1, 1, 2),
                 team = c("TL", "WIN", "NIP", "G2", 
                          "TSM", "EZ4", "PK", "RYE",
                          "NV", "M19", "DA", "REC",
                          "FC", "UT", "CC", "VIT"),
                 match = 45)
PEL_data <- bind_rows(PEL_data, PEL_45)

# match 46
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_4
PEL_46 <- tibble(placement_points = c(4, 0, 1, 10, 
                                      2, 1, 0, 0, 
                                      0, 6, 5, 3, 
                                      0, 0, 0, 0),
                 kill_points = c(3, 0, 8, 7, 
                                 7, 8, 4, 2, 
                                 3, 5, 1, 2, 
                                 2, 2, 1, 0),
                 team = c("TL", "WIN", "NIP", "G2", 
                          "TSM", "EZ4", "PK", "RYE",
                          "NV", "M19", "DA", "REC",
                          "FC", "UT", "CC", "VIT"),
                 match = 46)
PEL_data <- bind_rows(PEL_data, PEL_46)

# match 47
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_4
PEL_47 <- tibble(placement_points = c(0, 10, 1, 4, 
                                      6, 3, 0, 1, 
                                      2, 0, 0, 5, 
                                      0, 0, 0, 0),
                 kill_points = c(7, 12, 0, 1, 
                                 10, 1, 1, 5, 
                                 5, 1, 3, 3, 
                                 3, 4, 1, 1),
                 team = c("TL", "WIN", "NIP", "G2", 
                          "TSM", "EZ4", "PK", "RYE",
                          "NV", "M19", "DA", "REC",
                          "FC", "UT", "CC", "VIT"),
                 match = 47)
PEL_data <- bind_rows(PEL_data, PEL_47)

# match 48
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_4
PEL_48 <- tibble(placement_points = c(10, 0, 2, 0, 
                                      0, 6, 5, 0, 
                                      0, 0, 3, 1, 
                                      0, 1, 4, 0),
                 kill_points = c(17, 4, 3, 0, 
                                 2, 6, 8, 4, 
                                 2, 3, 2, 0, 
                                 1, 4, 1, 0),
                 team = c("TL", "WIN", "NIP", "G2", 
                          "TSM", "EZ4", "PK", "RYE",
                          "NV", "M19", "DA", "REC",
                          "FC", "UT", "CC", "VIT"),
                 match = 48)
PEL_data <- bind_rows(PEL_data, PEL_48)

# match 49
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_5
PEL_49 <- tibble(placement_points = c(10, 6, 0, 1, 
                                      0, 0, 2, 1, 
                                      5, 4, 0, 0, 
                                      0, 3, 0, 0),
                 kill_points = c(13, 5, 2, 5, 
                                 4, 1, 1, 5, 
                                 4, 2, 2, 5, 
                                 2, 3, 1, 3),
                 team = c("FC", "RYE", "G2", "TSM", 
                          "NIP", "NV", "REC", "PK",
                          "DA", "TL", "WIN", "UT",
                          "CC", "M19", "EZ4", "VIT"),
                 match = 49)
PEL_data <- bind_rows(PEL_data, PEL_49)

# match 50
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_5
PEL_50 <- tibble(placement_points = c(10, 5, 0, 6, 
                                      0, 4, 0, 3, 
                                      0, 1, 1, 2, 
                                      0, 0, 0, 0),
                 kill_points = c(9, 10, 2, 13, 
                                 1, 3, 1, 3, 
                                 2, 2, 2, 2, 
                                 5, 2, 4, 0),
                 team = c("FC", "RYE", "G2", "TSM", 
                          "NIP", "NV", "REC", "PK",
                          "DA", "TL", "WIN", "UT",
                          "CC", "M19", "EZ4", "VIT"),
                 match = 50)
PEL_data <- bind_rows(PEL_data, PEL_50)

# match 51
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_5
PEL_51 <- tibble(placement_points = c(0, 1, 4, 0, 
                                      3, 5, 10, 2, 
                                      6, 1, 0, 0, 
                                      0, 0, 0, 0),
                 kill_points = c(4, 3, 8, 3, 
                                 2, 4, 8, 1, 
                                 5, 9, 4, 4, 
                                 2, 1, 0, 1),
                 team = c("FC", "RYE", "G2", "TSM", 
                          "NIP", "NV", "REC", "PK",
                          "DA", "TL", "WIN", "UT",
                          "CC", "M19", "EZ4", "VIT"),
                 match = 51)
PEL_data <- bind_rows(PEL_data, PEL_51)

# match 52
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_5
PEL_52 <- tibble(placement_points = c(0, 5, 10, 3, 
                                      6, 2, 0, 4, 
                                      0, 0, 1, 0, 
                                      1, 0, 0, 0),
                 kill_points = c(4, 9, 13, 0, 
                                 12, 6, 2, 4, 
                                 0, 0, 6, 2, 
                                 3, 0, 0, 0),
                 team = c("FC", "RYE", "G2", "TSM", 
                          "NIP", "NV", "REC", "PK",
                          "DA", "TL", "WIN", "UT",
                          "CC", "M19", "EZ4", "VIT"),
                 match = 52)
PEL_data <- bind_rows(PEL_data, PEL_52)

# match 53
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_5
PEL_53 <- tibble(placement_points = c(5, 10, 6, 2, 
                                      4, 0, 0, 3, 
                                      0, 0, 1, 1, 
                                      0, 0, 0, 0),
                 kill_points = c(12, 15, 5, 4, 
                                 3, 0, 1, 8, 
                                 0, 0, 3, 4, 
                                 0, 1, 2, 0),
                 team = c("PK", "CC", "G2", "NV", 
                          "DA", "WIN", "VIT", "TSM",
                          "TL", "RYE", "REC", "M19",
                          "EZ4", "UT", "FC", "NIP"),
                 match = 53)
PEL_data <- bind_rows(PEL_data, PEL_53)

# match 54
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_5
PEL_54 <- tibble(placement_points = c(2, 0, 3, 6, 
                                      0, 5, 0, 0, 
                                      10, 1, 0, 4, 
                                      0, 0, 1, 0),
                 kill_points = c(4, 3, 4, 9, 
                                 0, 7, 0, 1, 
                                 8, 3, 7, 4, 
                                 2, 2, 2, 4),
                 team = c("PK", "CC", "G2", "NV", 
                          "DA", "WIN", "VIT", "TSM",
                          "TL", "RYE", "REC", "M19",
                          "EZ4", "UT", "FC", "NIP"),
                 match = 54)
PEL_data <- bind_rows(PEL_data, PEL_54)

# match 55
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_5
PEL_55 <- tibble(placement_points = c(4, 2, 0, 1, 
                                      3, 0, 10, 5, 
                                      0, 6, 0, 0, 
                                      0, 0, 0, 1),
                 kill_points = c(8, 4, 4, 6, 
                                 2, 5, 11, 1, 
                                 0, 3, 1, 0, 
                                 1, 5, 4, 2),
                 team = c("PK", "CC", "G2", "NV", 
                          "DA", "WIN", "VIT", "TSM",
                          "TL", "RYE", "REC", "M19",
                          "EZ4", "UT", "FC", "NIP"),
                 match = 55)
PEL_data <- bind_rows(PEL_data, PEL_55)

# match 56
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_5
PEL_56 <- tibble(placement_points = c(4, 1, 5, 2, 
                                      10, 6, 1, 0, 
                                      0, 0, 0, 0, 
                                      3, 0, 0, 0),
                 kill_points = c(7, 4, 8, 3, 
                                 10, 7, 4, 1, 
                                 0, 4, 3, 1, 
                                 4, 1, 0, 2),
                 team = c("PK", "CC", "G2", "NV", 
                          "DA", "WIN", "VIT", "TSM",
                          "TL", "RYE", "REC", "M19",
                          "EZ4", "UT", "FC", "NIP"),
                 match = 56)
PEL_data <- bind_rows(PEL_data, PEL_56)

# match 57
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_5
PEL_57 <- tibble(placement_points = c(6, 5, 0, 0, 
                                      3, 0, 10, 0, 
                                      0, 1, 4, 1, 
                                      2, 0, 0, 0),
                 kill_points = c(14, 8, 2, 5, 
                                 8, 1, 3, 2, 
                                 6, 4, 2, 2, 
                                 2, 0, 3, 1),
                 team = c("M19", "TL", "NV", "G2", 
                          "PK", "NIP", "REC", "FC",
                          "UT", "RYE", "DA", "CC",
                          "WIN", "TSM", "EZ4", "VIT"),
                 match = 57)
PEL_data <- bind_rows(PEL_data, PEL_57)

# match 58
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_5
PEL_58 <- tibble(placement_points = c(3, 0, 5, 10, 
                                      0, 0, 0, 2, 
                                      1, 6, 0, 1, 
                                      0, 4, 0, 0),
                 kill_points = c(7, 4, 5, 6, 
                                 3, 1, 5, 3, 
                                 5, 3, 1, 2, 
                                 3, 3, 1, 0),
                 team = c("M19", "TL", "NV", "G2", 
                          "PK", "NIP", "REC", "FC",
                          "UT", "RYE", "DA", "CC",
                          "WIN", "TSM", "EZ4", "VIT"),
                 match = 58)
PEL_data <- bind_rows(PEL_data, PEL_58)

# match 59
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_5
PEL_59 <- tibble(placement_points = c(1, 4, 6, 2, 
                                      5, 10, 0, 0, 
                                      0, 0, 1, 0, 
                                      0, 0, 0, 3),
                 kill_points = c(3, 11, 9, 5, 
                                 5, 8, 1, 10, 
                                 0, 0, 2, 1, 
                                 0, 1, 1, 1),
                 team = c("M19", "TL", "NV", "G2", 
                          "PK", "NIP", "REC", "FC",
                          "UT", "RYE", "DA", "CC",
                          "WIN", "TSM", "EZ4", "VIT"),
                 match = 59)
PEL_data <- bind_rows(PEL_data, PEL_59)

# match 60
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_5
PEL_60 <- tibble(placement_points = c(10, 6, 5, 0, 
                                      0, 0, 0, 2, 
                                      1, 0, 3, 4, 
                                      1, 0, 0, 0),
                 kill_points = c(12, 10, 8, 1, 
                                 2, 2, 2, 1, 
                                 5, 3, 2, 3, 
                                 3, 2, 3, 3),
                 team = c("M19", "TL", "NV", "G2", 
                          "PK", "NIP", "REC", "FC",
                          "UT", "RYE", "DA", "CC",
                          "WIN", "TSM", "EZ4", "VIT"),
                 match = 60)
PEL_data <- bind_rows(PEL_data, PEL_60)

# match 61
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_6
PEL_61 <- tibble(placement_points = c(10, 0, 6, 2, 
                                      4, 3, 0, 1, 
                                      0, 0, 5, 0, 
                                      1, 0, 0, 0),
                 kill_points = c(10, 1, 7, 6, 
                                 3, 2, 3, 3, 
                                 4, 3, 6, 0, 
                                 4, 1, 3, 2),
                 team = c("WIN", "TL", "TSM", "UT", 
                          "NV", "G2", "FC", "NIP",
                          "REC", "EZ4", "RYE", "M19",
                          "DA", "CC", "PK", "VIT"),
                 match = 61)
PEL_data <- bind_rows(PEL_data, PEL_61)

# match 62
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_6
PEL_62 <- tibble(placement_points = c(10, 1, 3, 0, 
                                      4, 0, 0, 6, 
                                      1, 0, 0, 2, 
                                      5, 0, 0, 0),
                 kill_points = c(7, 8, 3, 2, 
                                 4, 6, 2, 10, 
                                 5, 1, 1, 1, 
                                 3, 4, 1, 0),
                 team = c("WIN", "TL", "TSM", "UT", 
                          "NV", "G2", "FC", "NIP",
                          "REC", "EZ4", "RYE", "M19",
                          "DA", "CC", "PK", "VIT"),
                 match = 62)
PEL_data <- bind_rows(PEL_data, PEL_62)

# match 63
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_6
PEL_63 <- tibble(placement_points = c(5, 3, 1, 0, 
                                      4, 6, 10, 0, 
                                      2, 0, 0, 0, 
                                      0, 0, 0, 1),
                 kill_points = c(4, 13, 2, 1, 
                                 7, 6, 8, 0, 
                                 2, 5, 3, 2, 
                                 0, 1, 2, 3),
                 team = c("WIN", "TL", "TSM", "UT", 
                          "NV", "G2", "FC", "NIP",
                          "REC", "EZ4", "RYE", "M19",
                          "DA", "CC", "PK", "VIT"),
                 match = 63)
PEL_data <- bind_rows(PEL_data, PEL_63)

# match 64
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_6
PEL_64 <- tibble(placement_points = c(5, 6, 3, 10, 
                                      1, 2, 0, 0, 
                                      4, 0, 0, 1, 
                                      0, 0, 0, 0),
                 kill_points = c(4, 11, 9, 9, 
                                 2, 3, 0, 2, 
                                 4, 8, 1, 7, 
                                 0, 1, 1, 0),
                 team = c("WIN", "TL", "TSM", "UT", 
                          "NV", "G2", "FC", "NIP",
                          "REC", "EZ4", "RYE", "M19",
                          "DA", "CC", "PK", "VIT"),
                 match = 64)
PEL_data <- bind_rows(PEL_data, PEL_64)

# match 65
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_6
PEL_65 <- tibble(placement_points = c(0, 4, 0, 0, 
                                      5, 1, 10, 2, 
                                      1, 0, 0, 6, 
                                      0, 3, 0, 0),
                 kill_points = c(3, 3, 3, 2, 
                                 11, 5, 10, 2, 
                                 4, 0, 1, 2, 
                                 7, 3, 0, 3),
                 team = c("NV", "RYE", "CC", "PK", 
                          "G2", "FC", "VIT", "REC",
                          "WIN", "TL", "EZ4", "UT",
                          "NIP", "M19", "DA", "TSM"),
                 match = 65)
PEL_data <- bind_rows(PEL_data, PEL_65)

# match 66
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_6
PEL_66 <- tibble(placement_points = c(6, 10, 0, 2, 
                                      0, 4, 0, 0, 
                                      5, 1, 0, 1, 
                                      0, 0, 3, 0),
                 kill_points = c(10, 8, 0, 10, 
                                 1, 5, 3, 4, 
                                 3, 5, 3, 1, 
                                 2, 1, 2, 1),
                 team = c("NV", "RYE", "CC", "PK", 
                          "G2", "FC", "VIT", "REC",
                          "WIN", "TL", "EZ4", "UT",
                          "NIP", "M19", "DA", "TSM"),
                 match = 66)
PEL_data <- bind_rows(PEL_data, PEL_66)

# match 67
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_6
PEL_67 <- tibble(placement_points = c(0, 0, 10, 1, 
                                      2, 0, 0, 6, 
                                      0, 5, 3, 0, 
                                      0, 4, 0, 1),
                 kill_points = c(2, 2, 14, 3, 
                                 4, 1, 0, 7, 
                                 4, 7, 1, 3, 
                                 1, 2, 6, 2),
                 team = c("NV", "RYE", "CC", "PK", 
                          "G2", "FC", "VIT", "REC",
                          "WIN", "TL", "EZ4", "UT",
                          "NIP", "M19", "DA", "TSM"),
                 match = 67)
PEL_data <- bind_rows(PEL_data, PEL_67)

# match 68
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_6
PEL_68 <- tibble(placement_points = c(10, 3, 0, 5, 
                                      6, 2, 0, 0, 
                                      0, 0, 4, 0, 
                                      1, 0, 0, 1),
                 kill_points = c(7, 8, 6, 9, 
                                 3, 8, 1, 2, 
                                 2, 0, 6, 2, 
                                 3, 1, 0, 2),
                 team = c("NV", "RYE", "CC", "PK", 
                          "G2", "FC", "VIT", "REC",
                          "WIN", "TL", "EZ4", "UT",
                          "NIP", "M19", "DA", "TSM"),
                 match = 68)
PEL_data <- bind_rows(PEL_data, PEL_68)

# match 69
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_6
PEL_69 <- tibble(placement_points = c(6, 10, 0, 2, 
                                      0, 0, 3, 0, 
                                      4, 5, 1, 0, 
                                      0, 0, 1, 0),
                 kill_points = c(10, 10, 4, 1, 
                                 2, 4, 8, 1, 
                                 5, 5, 1, 1, 
                                 1, 3, 2, 1),
                 team = c("NV", "G2", "DA", "TSM", 
                          "TL", "UT", "CC", "FC",
                          "WIN", "REC", "PK", "RYE",
                          "EZ4", "NIP", "VIT", "M19"),
                 match = 69)
PEL_data <- bind_rows(PEL_data, PEL_69)

# match 70
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_6
PEL_70 <- tibble(placement_points = c(0, 10, 1, 0, 
                                      4, 0, 0, 5, 
                                      2, 0, 0, 3, 
                                      6, 0, 1, 0),
                 kill_points = c(1, 7, 6, 3, 
                                 0, 0, 4, 10, 
                                 8, 2, 0, 6, 
                                 4, 5, 0, 1),
                 team = c("NV", "G2", "DA", "TSM", 
                          "TL", "UT", "CC", "FC",
                          "WIN", "REC", "PK", "RYE",
                          "EZ4", "NIP", "VIT", "M19"),
                 match = 70)
PEL_data <- bind_rows(PEL_data, PEL_70)

# match 71
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_6
PEL_71 <- tibble(placement_points = c(5, 0, 6, 2, 
                                      3, 10, 0, 0, 
                                      1, 0, 4, 1, 
                                      0, 0, 0, 0),
                 kill_points = c(9, 1, 10, 4, 
                                 8, 8, 4, 1, 
                                 2, 2, 3, 1, 
                                 0, 1, 3, 2),
                 team = c("NV", "G2", "DA", "TSM", 
                          "TL", "UT", "CC", "FC",
                          "WIN", "REC", "PK", "RYE",
                          "EZ4", "NIP", "VIT", "M19"),
                 match = 71)
PEL_data <- bind_rows(PEL_data, PEL_71)

# match 72
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_6
PEL_72 <- tibble(placement_points = c(5, 1, 4, 10, 
                                      6, 0, 0, 1, 
                                      0, 3, 2, 0, 
                                      0, 0, 0, 0),
                 kill_points = c(9, 4, 2, 8, 
                                 5, 4, 3, 4, 
                                 0, 1, 3, 1, 
                                 2, 1, 2, 4),
                 team = c("NV", "G2", "DA", "TSM", 
                          "TL", "UT", "CC", "FC",
                          "WIN", "REC", "PK", "RYE",
                          "EZ4", "NIP", "VIT", "M19"),
                 match = 72)
PEL_data <- bind_rows(PEL_data, PEL_72)

# match 73
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_7
PEL_73 <- tibble(placement_points = c(10, 5, 0, 0, 
                                      2, 6, 0, 0, 
                                      3, 1, 0, 0, 
                                      4, 0, 1, 0),
                 kill_points = c(12, 6, 2, 0, 
                                 9, 7, 2, 0, 
                                 3, 0, 1, 1, 
                                 8, 1, 3, 1),
                 team = c("M19", "FC", "VIT", "TSM", 
                          "TL", "NV", "REC", "PK",
                          "NIP", "RYE", "EZ4", "G2",
                          "DA", "CC", "WIN", "UT"),
                 match = 73)
PEL_data <- bind_rows(PEL_data, PEL_73)

# match 74
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_7
PEL_74 <- tibble(placement_points = c(0, 3, 5, 2, 
                                      0, 0, 1, 1, 
                                      6, 4, 0, 10, 
                                      0, 0, 0, 0),
                 kill_points = c(4, 7, 5, 7, 
                                 1, 4, 4, 4, 
                                 6, 4, 0, 6, 
                                 2, 0, 1, 2),
                 team = c("M19", "FC", "VIT", "TSM", 
                          "TL", "NV", "REC", "PK",
                          "NIP", "RYE", "EZ4", "G2",
                          "DA", "CC", "WIN", "UT"),
                 match = 74)
PEL_data <- bind_rows(PEL_data, PEL_74)

# match 75
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_7
PEL_75 <- tibble(placement_points = c(2, 6, 0, 1, 
                                      0, 0, 5, 0, 
                                      0, 3, 10, 0, 
                                      0, 4, 1, 0),
                 kill_points = c(6, 8, 1, 7, 
                                 0, 4, 6, 2, 
                                 0, 9, 9, 1, 
                                 0, 5, 0, 1),
                 team = c("M19", "FC", "VIT", "TSM", 
                          "TL", "NV", "REC", "PK",
                          "NIP", "RYE", "EZ4", "G2",
                          "DA", "CC", "WIN", "UT"),
                 match = 75)
PEL_data <- bind_rows(PEL_data, PEL_75)

# match 76
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_7
PEL_76 <- tibble(placement_points = c(2, 0, 10, 5, 
                                      4, 1, 3, 6, 
                                      0, 0, 0, 0, 
                                      1, 0, 0, 0),
                 kill_points = c(3, 1, 11, 6, 
                                 9, 3, 3, 10, 
                                 5, 1, 0, 1, 
                                 0, 4, 0, 0),
                 team = c("M19", "FC", "VIT", "TSM", 
                          "TL", "NV", "REC", "PK",
                          "NIP", "RYE", "EZ4", "G2",
                          "DA", "CC", "WIN", "UT"),
                 match = 76)
PEL_data <- bind_rows(PEL_data, PEL_76)

# match 77
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_7
PEL_77 <- tibble(placement_points = c(5, 0, 4, 6, 
                                      10, 3, 0, 0, 
                                      2, 0, 0, 1, 
                                      0, 1, 0, 0),
                 kill_points = c(9, 4, 5, 4, 
                                 16, 3, 3, 0, 
                                 6, 0, 0, 1, 
                                 1, 1, 2, 4),
                 team = c("VIT", "PK", "EZ4", "TL", 
                          "G2", "FC", "NIP", "TSM",
                          "UT", "WIN", "REC", "DA",
                          "CC", "NV", "M19", "RYE"),
                 match = 77)
PEL_data <- bind_rows(PEL_data, PEL_77)

# match 78
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_7
PEL_78 <- tibble(placement_points = c(0, 4, 10, 0, 
                                      0, 1, 1, 5, 
                                      0, 6, 0, 3, 
                                      0, 2, 0, 0),
                 kill_points = c(1, 6, 4, 5, 
                                 0, 4, 7, 9, 
                                 3, 8, 2, 5, 
                                 1, 3, 0, 1),
                 team = c("VIT", "PK", "EZ4", "TL", 
                          "G2", "FC", "NIP", "TSM",
                          "UT", "WIN", "REC", "DA",
                          "CC", "NV", "M19", "RYE"),
                 match = 78)
PEL_data <- bind_rows(PEL_data, PEL_78)

# match 79
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_7
PEL_79 <- tibble(placement_points = c(10, 0, 0, 1, 
                                      0, 6, 3, 1, 
                                      5, 2, 4, 0, 
                                      0, 0, 0, 0),
                 kill_points = c(11, 0, 6, 2, 
                                 0, 2, 8, 4, 
                                 6, 4, 10, 0, 
                                 0, 2, 4, 0),
                 team = c("VIT", "PK", "EZ4", "TL", 
                          "G2", "FC", "NIP", "TSM",
                          "UT", "WIN", "REC", "DA",
                          "CC", "NV", "M19", "RYE"),
                 match = 79)
PEL_data <- bind_rows(PEL_data, PEL_79)

# match 80
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_7
PEL_80 <- tibble(placement_points = c(0, 10, 3, 5, 
                                      0, 4, 1, 0, 
                                      0, 1, 0, 2, 
                                      6, 0, 0, 0),
                 kill_points = c(3, 10, 1, 6, 
                                 1, 4, 3, 5, 
                                 2, 2, 4, 5, 
                                 7, 3, 2, 1),
                 team = c("VIT", "PK", "EZ4", "TL", 
                          "G2", "FC", "NIP", "TSM",
                          "UT", "WIN", "REC", "DA",
                          "CC", "NV", "M19", "RYE"),
                 match = 80)
PEL_data <- bind_rows(PEL_data, PEL_80)

# match 81
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_7
PEL_81 <- tibble(placement_points = c(0, 10, 5, 0, 
                                      3, 0, 6, 0, 
                                      0, 1, 2, 0, 
                                      0, 0, 1, 4),
                 kill_points = c(4, 13, 4, 1, 
                                 4, 0, 8, 0, 
                                 1, 3, 7, 3, 
                                 0, 2, 4, 1),
                 team = c("EZ4", "NIP", "FC", "CC", 
                          "M19", "REC", "VIT", "TL",
                          "G2", "RYE", "UT", "TSM",
                          "PK", "NV", "WIN", "DA"),
                 match = 81)
PEL_data <- bind_rows(PEL_data, PEL_81)

# match 82
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_7
PEL_82 <- tibble(placement_points = c(6, 0, 10, 5, 
                                      1, 0, 1, 3, 
                                      0, 0, 0, 0, 
                                      4, 0, 0, 2),
                 kill_points = c(5, 1, 13, 7, 
                                 5, 2, 1, 9, 
                                 7, 1, 4, 0, 
                                 2, 1, 2, 0),
                 team = c("EZ4", "NIP", "FC", "CC", 
                          "M19", "REC", "VIT", "TL",
                          "G2", "RYE", "UT", "TSM",
                          "PK", "NV", "WIN", "DA"),
                 match = 82)
PEL_data <- bind_rows(PEL_data, PEL_82)

# match 83
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_7
PEL_83 <- tibble(placement_points = c(3, 6, 0, 2, 
                                      5, 10, 0, 0, 
                                      1, 0, 0, 4, 
                                      0, 1, 0, 0),
                 kill_points = c(6, 6, 1, 6, 
                                 5, 12, 0, 0,
                                 8, 7, 1, 4, 
                                 3, 1, 1, 0),
                 team = c("EZ4", "NIP", "FC", "CC", 
                          "M19", "REC", "VIT", "TL",
                          "G2", "RYE", "UT", "TSM",
                          "PK", "NV", "WIN", "DA"),
                 match = 83)
PEL_data <- bind_rows(PEL_data, PEL_83)

# match 84
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_7
PEL_84 <- tibble(placement_points = c(10, 4, 0, 6, 
                                      1, 3, 0, 5, 
                                      0, 1, 0, 0, 
                                      2, 0, 0, 0),
                 kill_points = c(10, 2, 8, 8, 
                                 9, 0, 7, 4, 
                                 3, 2, 0, 2, 
                                 1, 4, 0, 0),
                 team = c("EZ4", "NIP", "FC", "CC", 
                          "M19", "REC", "VIT", "TL",
                          "G2", "RYE", "UT", "TSM",
                          "PK", "NV", "WIN", "DA"),
                 match = 84)
PEL_data <- bind_rows(PEL_data, PEL_84)

# match 85
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_8
PEL_85 <- tibble(placement_points = c(10, 5, 6, 1, 
                                      0, 0, 2, 4, 
                                      0, 1, 0, 0, 
                                      0, 0, 0, 3),
                 kill_points = c(13, 0, 5, 7, 
                                 7, 0, 3, 10, 
                                 3, 2, 0, 1, 
                                 5, 0, 0, 3),
                 team = c("REC", "G2", "EZ4", "TL", 
                          "PK", "DA", "CC", "RYE",
                          "WIN", "UT", "NV", "VIT",
                          "FC", "TSM", "NIP", "M19"),
                 match = 85)
PEL_data <- bind_rows(PEL_data, PEL_85)

# match 86
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_8
PEL_86 <- tibble(placement_points = c(0, 0, 0, 0, 
                                      5, 10, 0, 3, 
                                      0, 6, 4, 2, 
                                      0, 1, 1, 0),
                 kill_points = c(4, 0, 1, 10, 
                                 8, 6, 1, 8, 
                                 0, 6, 1, 3, 
                                 4, 2, 3, 1),
                 team = c("REC", "G2", "EZ4", "TL", 
                          "PK", "DA", "CC", "RYE",
                          "WIN", "UT", "NV", "VIT",
                          "FC", "TSM", "NIP", "M19"),
                 match = 86)
PEL_data <- bind_rows(PEL_data, PEL_86)

# match 87
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_8
PEL_87 <- tibble(placement_points = c(4, 10, 1, 3, 
                                      6, 5, 0, 0, 
                                      2, 0, 0, 1, 
                                      0, 0, 0, 0),
                 kill_points = c(4, 8, 7, 1, 
                                 2, 9, 5, 0, 
                                 5, 1, 1, 6, 
                                 2, 2, 5, 0),
                 team = c("REC", "G2", "EZ4", "TL", 
                          "PK", "DA", "CC", "RYE",
                          "WIN", "UT", "NV", "VIT",
                          "FC", "TSM", "NIP", "M19"),
                 match = 87)
PEL_data <- bind_rows(PEL_data, PEL_87)

# match 88
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_8
PEL_88 <- tibble(placement_points = c(1, 2, 6, 1, 
                                      0, 0, 5, 0, 
                                      10, 0, 3, 0, 
                                      0, 4, 0, 0),
                 kill_points = c(2, 8, 6, 8, 
                                 2, 0, 12, 2, 
                                 7, 3, 5, 0, 
                                 1, 2, 1, 2),
                 team = c("REC", "G2", "EZ4", "TL", 
                          "PK", "DA", "CC", "RYE",
                          "WIN", "UT", "NV", "VIT",
                          "FC", "TSM", "NIP", "M19"),
                 match = 88)
PEL_data <- bind_rows(PEL_data, PEL_88)

# match 89
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_8
PEL_89 <- tibble(placement_points = c(0, 1, 4, 10, 
                                      2, 3, 0, 5, 
                                      6, 0, 0, 0, 
                                      1, 0, 0, 0),
                 kill_points = c(5, 3, 6, 14, 
                                 1, 1, 2, 0, 
                                 9, 3, 4, 3, 
                                 2, 4, 0, 0),
                 team = c("EZ4", "DA", "CC", "TSM", 
                          "REC", "VIT", "FC", "NIP",
                          "TL", "WIN", "M19", "PK",
                          "G2", "NV", "RYE", "UT"),
                 match = 89)
PEL_data <- bind_rows(PEL_data, PEL_89)

# match 90
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_8
PEL_90 <- tibble(placement_points = c(10, 4, 0, 0, 
                                      0, 5, 0, 2, 
                                      0, 1, 6, 0, 
                                      0, 1, 0, 3),
                 kill_points = c(13, 0, 2, 3, 
                                 2, 9, 0, 8, 
                                 1, 1, 6, 3, 
                                 0, 1, 6, 3),
                 team = c("EZ4", "DA", "CC", "TSM", 
                          "REC", "VIT", "FC", "NIP",
                          "TL", "WIN", "M19", "PK",
                          "G2", "NV", "RYE", "UT"),
                 match = 90)
PEL_data <- bind_rows(PEL_data, PEL_90)

# match 91
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_8
PEL_91 <- tibble(placement_points = c(4, 6, 3, 0, 
                                      1, 2, 10, 0, 
                                      1, 0, 0, 5, 
                                      0, 0, 0, 0),
                 kill_points = c(6, 7, 4, 2, 
                                 9, 5, 8, 4, 
                                 5, 0, 0, 4, 
                                 4, 0, 0, 1),
                 team = c("EZ4", "DA", "CC", "TSM", 
                          "REC", "VIT", "FC", "NIP",
                          "TL", "WIN", "M19", "PK",
                          "G2", "NV", "RYE", "UT"),
                 match = 91)
PEL_data <- bind_rows(PEL_data, PEL_91)

# match 92
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_8
PEL_92 <- tibble(placement_points = c(0, 6, 5, 0, 
                                      3, 0, 1, 0, 
                                      0, 10, 0, 1, 
                                      4, 2, 0, 0),
                 kill_points = c(1, 10, 9, 2, 
                                 9, 1, 3, 4, 
                                 0, 7, 2, 1, 
                                 5, 6, 2, 0),
                 team = c("EZ4", "DA", "CC", "TSM", 
                          "REC", "VIT", "FC", "NIP",
                          "TL", "WIN", "M19", "PK",
                          "G2", "NV", "RYE", "UT"),
                 match = 92)
PEL_data <- bind_rows(PEL_data, PEL_92)

# match 93
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_8
PEL_93 <- tibble(placement_points = c(10, 1, 3, 5, 
                                      0, 0, 4, 0, 
                                      6, 0, 1, 0, 
                                      0, 2, 0, 0),
                 kill_points = c(9, 15, 7, 2, 
                                 0, 2, 4, 0, 
                                 7, 1, 2, 2, 
                                 5, 2, 2, 0),
                 team = c("PK", "CC", "FC", "REC", 
                          "NIP", "TSM", "VIT", "NV",
                          "TL", "RYE", "EZ4", "DA",
                          "UT", "G2", "WIN", "M19"),
                 match = 93)
PEL_data <- bind_rows(PEL_data, PEL_93)

# match 94
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_8
PEL_94 <- tibble(placement_points = c(10, 4, 0, 1, 
                                      5, 0, 0, 3, 
                                      0, 6, 1, 2, 
                                      0, 0, 0, 0),
                 kill_points = c(12, 12, 0, 6, 
                                 7, 5, 1, 0, 
                                 0, 6, 0, 6, 
                                 1, 3, 0, 0),
                 team = c("PK", "CC", "FC", "REC", 
                          "NIP", "TSM", "VIT", "NV",
                          "TL", "RYE", "EZ4", "DA",
                          "UT", "G2", "WIN", "M19"),
                 match = 94)
PEL_data <- bind_rows(PEL_data, PEL_94)

# match 95
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_8
PEL_95 <- tibble(placement_points = c(4, 1, 10, 5, 
                                      2, 6, 0, 1,
                                      0, 3, 0, 0, 
                                      0, 0, 0, 0),
                 kill_points = c(9, 4, 0, 7, 
                                 7, 7, 3, 3, 
                                 0, 1, 5, 0, 
                                 1, 1, 1, 1),
                 team = c("PK", "CC", "FC", "REC", 
                          "NIP", "TSM", "VIT", "NV",
                          "TL", "RYE", "EZ4", "DA",
                          "UT", "G2", "WIN", "M19"),
                 match = 95)
PEL_data <- bind_rows(PEL_data, PEL_95)

# match 96
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2/Week_8
PEL_96 <- tibble(placement_points = c(10, 0, 5, 1, 
                                      0, 0, 3, 6, 
                                      0, 0, 1, 2, 
                                      4, 0, 0, 0),
                 kill_points = c(11, 1, 9, 4, 
                                 3, 2, 7, 6, 
                                 4, 0, 4, 2, 
                                 3, 0, 2, 3),
                 team = c("PK", "CC", "FC", "REC", 
                          "NIP", "TSM", "VIT", "NV",
                          "TL", "RYE", "EZ4", "DA",
                          "UT", "G2", "WIN", "M19"),
                 match = 96)
PEL_data <- bind_rows(PEL_data, PEL_96)

glimpse(PEL_data)

# calculate total points, cumulative points, and cumulative average points per match

PEL_data %<>%
  mutate(points = placement_points + kill_points) %>%
  group_by(team) %>%
  mutate(cumulative_points = cumsum(points)) %>%
  mutate(cumulative_avg_points = cumulative_points / match) %>%
  ungroup()

print(PEL_data, n = 200) # verify cumulative average is correct
 
```

&#x200B;

Phase 2 of PUBG Europe League has wrapped up after a tense final weekend. I thought I'd share an overview of **how each team performed throughout the phase.**

&#x200B;

**TRENDS IN THE STANDINGS**

&#x200B;

Similarly to how I plotted [trends in the standings over NPL Phase 2](https://pubgdataviz.netlify.com/post/2019-06-14-phase-2-overview/), I made an **interactive tool to look at each teams results over PEL Phase 2.**

I cropped this plotly visualization fairly tightly so there's more detail visible for the last few weeks, but zoom out with the controls in the upper right to see the chaos at the beginning of the phase, with G2 and CrowCrowd having great matches to start out, and Team Liquid bouncing back from a zero-point match with a 20-point win. 

Hover over the colored lines in the plot to see **details for how each team's average points changed with each match.** Use the pan tool to move around. Double click on a team name in the legend to **isolate that team's trendline**, and single click to **add or remove other teams trendlines to compare**. Double click again or press the home button in the upper right to restore the plot to defaults.

&#x200B;

``` {r time_series, echo = FALSE, message = FALSE, fig.keep = 'all', fig.height = 6, fig.width = 8}

PEL_data$team <- factor(PEL_data$team, levels = c("FC", "NV", "TL", "G2", 
                                               "PK", "TSM", "CC", "NIP", 
                                               "RYE", "DA", "EZ4", "WIN", 
                                               "REC", "VIT", "M19", "UT"))
team_colors <- c("tomato3", "yellow", "dodgerblue4", "brown4",
                 "darkgoldenrod4", "black", "lightseagreen", "cornsilk4", #darkturquoise? #peachpuff4?
                 "chocolate2", "deepskyblue4", "burlywood4", "deeppink3", 
                 "orangered4", "gold3", "red3", "turquoise4")

p <- ggplot(PEL_data,
       aes(x = match, 
           y = cumulative_avg_points,
           colour = team,
           group = team,
           text = sprintf('Match: %s\nCumulative Average Points: %s\nTeam: %s', 
                          PEL_data$match, 
                          round(PEL_data$cumulative_avg_points, 
                                digits = 3),
                          PEL_data$team))) +
       geom_line(size = 0.7) +
  labs(x = "Match", 
       y = "Cumulative Average Points per Match") +
  scale_x_continuous(limit = c(1, 96),
                     expand = c(0, 0)) +
  scale_y_continuous(limit = c(0, 24),
                     expand = c(0, 0)) +
  coord_cartesian(xlim = c(1, 96),
                  ylim = c(3, 9)) +
  scale_colour_manual(values = team_colors) +
  theme_bw() +
  theme(axis.title.y = element_text(margin = margin(r = 20)),
        axis.title.x = element_text(margin = margin(t = 20)),
        text = element_text(family = "Helvetica"),
        legend.title = element_blank())

pl <- ggplotly(p, tooltip = "text") %>%
  layout(hoverlabel = list(bgcolor = "white",
                           font = list(family = "Helvetica",
                                       size = 11,
                                       color = "gray10"))) %>%
  add_annotations(text = "Team", xref = "paper", yref = "paper",
                  x = 1.02, xanchor = "left",
                  y = 0.985, yanchor = "top",
                  legendtitle = TRUE, showarrow = FALSE) %>%
  layout(legend = list(y = 0.94, yanchor = "top"))

pl

```

&#x200B;

^*Figure 1: Interactive plot of team performance over the course of PEL Phase 2.*^

&#x200B;

"Cumulative average points" refers to a teams total standings points after a given match divided by the number of matches (average points), incremented over the increasing number of matches as time goes on (cumulatively). If I graphed total points over time, the plot would be this same mess but all in a diagonal line, so essentially **I just divided the ongoing points totals by the number of matches to make the plot more horizontal and easier to read.**

**The relative position of each team is accurate for each days results**, so you can see how the standings change over time.

It's clear from this plot that **the top teams separated out fairly early on**, although Team SoloMid slowly declined starting around the halfway point, making the contest for 5^th^ place more exciting near the end. 

Speaking of the end, **Pittsburgh Knights had an incredible 75-point performance in the final weekend to just barely take over that 5^th^ place spot**.

The top four teams shifted around over the final few matches as well, with Team Liquid and G2 declining slightly from their previous average performance, and Natus Vincere and FaZe Clan criss-crossing several times (zoom in on these four teams at the end to see more detail). FaZe had two good matches in a row right at the end to seal their first-place finish. 

NV seemed to have a steady drop in performance from match 73 on, while the other top teams were a bit more consistent.

In the lower half of the standings, CrowCrowd had a chaotic Phase 2, bumping up their average with a few great matches (53, 67). ENCE declined to a low point at match 74 and improved from there, and Vitality turned things around from there as well. Reciprocity continuously improved throughout the phase.

&#x200B;

**PARITY UPDATE**

&#x200B;

Now that Phase 2 of PEL and PEL-C is are complete, I've created an updated visualization of the parity metric I described in [my previous post](https://pubgdataviz.netlify.com/post/2019-07-03-parity/). If you missed it, **parity is the level of fairness or competitiveness in a league**. High parity means teams are more similar in terms of skill, and have a more equal chance of winning, which makes predicting the results more difficult.

&#x200B;

``` {r parity_data_setup, echo = FALSE, results = "hide", fig.height = 7.5, fig.width = 7.5}

# create a dataset containing the points spreads from all phases of all leagues internationally

# Taiwan: Master League 2019 - Phase 1: Finals 
# https://liquipedia.net/pubg/PUBG_Master_League/2019/Phase_1
ML1_finals_parity <- tibble(points = c(135, 133, 122, 100,
                                       100, 96, 94, 94,
                                       86, 71, 66, 62,
                                       55, 55, 45, 41),
                            phase = "ML1") # 15 matches 
# can't include the regular season because the league has 24 teams and a completely different format from other leagues
# so to have a good comparison i'm using only the finals with 16 teams
# although using the finals with only 15 matches introduces high variability with phase length... i wonder if parity is correlated with phase length (probably smh)

# start the global dataset
global_parity <- ML1_finals_parity

# Taiwan: Master League 2019 - Phase 2: Finals 
# https://liquipedia.net/pubg/PUBG_Master_League/2019/Phase_2
# not done until July 7

# AU & NZ: ESL AU & NZ Championship 2019 - Phase 1
# https://liquipedia.net/pubg/ESL/ANZ_Championship/Phase_1
ANZ1_parity <- tibble(points = c(386, 374, 208, 192, 
                                    183, 173, 170, 160, 
                                    160, 157, 137, 123, 
                                    118, 113, 111, 101),
                      phase = "ANZ1") # 32 matches
global_parity <- bind_rows(global_parity, ANZ1_parity)

# AU & NZ: ESL AU & NZ Championship 2019 - Phase 2
# https://liquipedia.net/pubg/ESL/ANZ_Championship/Phase_2
ANZ2_parity <- tibble(points = c(540, 322, 293, 263,
                                     253, 233, 226, 214,
                                     204, 203, 199, 197,
                                     156, 124, 98, 90),
                      phase = "ANZ2") # 40 matches 
global_parity <- bind_rows(global_parity, ANZ2_parity)

# PUBG Southeast Asia Championship 2019 - Phase 1
# https://liquipedia.net/pubg/PUBG_Southeast_Asia_Championship/2019/Phase_1
PSC1_parity <- tibble(points = c(124, 114, 103, 94, 
                                 93, 81, 76, 76, 
                                 51, 49, 46, 44, 
                                 42, 37, 31, 30),
                      phase = "PSC1") # 12 matches
global_parity <- bind_rows(global_parity, PSC1_parity)

# PUBG Southeast Asia Championship 2019 - Phase 2
# https://liquipedia.net/pubg/PUBG_Southeast_Asia_Championship/2019/Phase_2
PSC2_parity <- tibble(points = c(139, 104, 93, 93,
                                 84, 64, 64, 63, 
                                 59, 59, 57, 52,
                                 50, 46, 38, 30),
                      phase = "PSC2") # 12 matches
global_parity <- bind_rows(global_parity, PSC2_parity)

# PUBG Korea League 2019
# can't include because the league has 24 teams and a completely different format from other leagues

# PUBG Korea Contenders 2019 - Phase 1
# https://liquipedia.net/pubg/PUBG_Korea_Contenders/2019/Phase_1
PKC1_parity <- tibble(points = c(579, 395, 345, 319, 
                                 296, 260, 251, 248, 
                                 248, 245, 240, 219, 
                                 205, 200, 199, 80),
                      phase = "PKC1") # 48 matches
global_parity <- bind_rows(global_parity, PKC1_parity)

# PUBG Korea Contenders 2019 - Phase 2
# https://liquipedia.net/pubg/PUBG_Korea_Contenders/2019/Phase_2
# not done until July 7

# ESL LA League: Season 2
# ~ Phase 1
# https://liquipedia.net/pubg/ESL/LA_League/Season_2
LA1_parity <- tibble(points = c(294, 210, 194, 186, 
                                172, 170, 166, 127, 
                                105, 93, 88, 84, 
                                72, 72, 57, 52),
                     phase = "LA1") # 24 matches
global_parity <- bind_rows(global_parity, LA1_parity)

# ESL LA League: Season 3
# ~ Phase 2
# https://liquipedia.net/pubg/ESL/LA_League/Season_3
LA2_parity <- tibble(points = c(209, 180, 146, 142,
                                126, 126, 117, 112,
                                107, 98, 94, 77,
                                72, 63, 63, 61),
                     phase = "LA2") # 24 matches
global_parity <- bind_rows(global_parity, LA2_parity)

# PUBG JAPAN SERIES Season 2: Grade 1 - Phase 1
# https://liquipedia.net/pubg/PUBG_JAPAN_SERIES/Season_2/Phase_1/Grade_1
# essentially the first half of global phase 1
PJS1_1_parity <- tibble(points = c(110, 99, 97, 88, 
                                   79, 79, 78, 76, 
                                   71, 64, 50, 46, 
                                   40, 40, 36, 33),
                        phase = "PJS1") # 12 matches
global_parity <- bind_rows(global_parity, PJS1_1_parity)

# PUBG JAPAN SERIES Season 2: Grade 1 - Phase 2
# https://liquipedia.net/pubg/PUBG_JAPAN_SERIES/Season_2/Phase_2/Grade_1
# second half of global phase 1
PJS1_2_parity <- tibble(points = c(103, 96, 92, 92, 
                                   91, 84, 75, 70, 
                                   66, 63, 54, 50, 
                                   46, 41, 36, 29),
                        phase = "PJS2") # 12 matches
global_parity <- bind_rows(global_parity, PJS1_2_parity)

# PUBG JAPAN SERIES Season 3: Grade 1 - Phase 1
# https://liquipedia.net/pubg/PUBG_JAPAN_SERIES/Season_3/Phase_1/Grade_1
# first half of global phase 2
PJS2_1_parity <- tibble(points = c(133, 108, 90, 90,
                                   80, 68, 67, 64, 
                                   64, 61, 56, 50,
                                   38, 36, 35, 28),
                        phase = "PJS3") # 12 matches
global_parity <- bind_rows(global_parity, PJS2_1_parity)

# PUBG JAPAN SERIES Season 3: Grade 1 - Phase 1
# second half of global phase 2
# not completed yet

# PUBG JAPAN SERIES Season 2: Grade 2 - Phase 1
# first half of global phase 1
# https://liquipedia.net/pubg/PUBG_JAPAN_SERIES/Season_2/Phase_1/Grade_2
PJS21_1_parity <- tibble(points = c(105, 91, 89, 84, 
                                     76, 69, 68, 68, 
                                     67, 67, 62, 61, 
                                     58, 44, 42, 40),
                         phase = "PJSC1") # 12 matches
global_parity <- bind_rows(global_parity, PJS21_1_parity)

# PUBG JAPAN SERIES Season 2: Grade 2 - Phase 2
# second half of global phase 1
# https://liquipedia.net/pubg/PUBG_JAPAN_SERIES/Season_2/Phase_2/Grade_2
PJS21_2_parity <- tibble(points = c(138, 88, 83, 82, 
                                     82, 80, 74, 67, 
                                     64, 56, 52, 50, 
                                     50, 49, 41, 30),
                         phase = "PJSC2") # 12 matches
global_parity <- bind_rows(global_parity, PJS21_2_parity)

# PUBG JAPAN SERIES Season 3: Grade 2 - Phase 1
# first half of global phase 2
# https://liquipedia.net/pubg/PUBG_JAPAN_SERIES/Season_3/Phase_1/Grade_2
PJS22_1_parity <- tibble(points = c(122, 109, 91, 86, 
                                     79, 74, 73, 61, 
                                     61, 55, 52, 48, 
                                     48, 43, 37, 36),
                         phase = "PJSC3") # 12 matches
global_parity <- bind_rows(global_parity, PJS22_1_parity)

# PUBG JAPAN SERIES Season 3: Grade 2 - Phase 2
# second half of global phase 2
# https://liquipedia.net/pubg/PUBG_JAPAN_SERIES/Season_3/Phase_2/Grade_2
# to be completed July 12

# PUBG Champions League 2019
# Chinese league - has a round robin format with 48 teams so can't be compared

# PUBG Europe League - Phase 1
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_1
PEL1_parity <- tibble(points = c(496, 417, 390, 383, 
                                 382, 364, 362, 340, 
                                 337, 324, 317, 316, 
                                 315, 294, 196, 185),
                      phase = "PEL1") # 60 matches
global_parity <- bind_rows(global_parity, PEL1_parity)

# PUBG Europe League - Phase 2
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2
# to be completed July 7

# PUBG Europe League Contenders - Phase 1
# https://liquipedia.net/pubg/PUBG_Contenders_League/2019/Phase_1
PELC1_parity <- tibble(points = c(250, 216, 155, 149, 
                                  147, 146, 146, 140, 
                                  139, 131, 101, 98, 
                                  93, 91, 85, 73),
                       phase = "PELC1") # 48 matches
global_parity <- bind_rows(global_parity, PELC1_parity)

# PUBG Europe League Contenders - Phase 2
# https://liquipedia.net/pubg/PUBG_Contenders_League/2019/Phase_2
# to be completed July 4

# National PUBG League - Phase 1
# https://liquipedia.net/pubg/National_PUBG_League/2019/Phase_1
NPL1_parity <- tibble(points = c(368, 299, 290, 285,
                                 283, 232, 226, 220,
                                 216, 211, 211, 182,
                                 176, 142, 140, 126),
                      phase = "NPL1") # 40 matches
global_parity <- bind_rows(global_parity, NPL1_parity)

# National PUBG League - Phase 2
# https://liquipedia.net/pubg/National_PUBG_League/2019/Phase_2
NPL2_parity <- tibble(points = c(296, 285, 284, 274,
                                 273, 244, 238, 237,
                                 235, 224, 203, 194,
                                 192, 154, 149, 139),
                      phase = "NPL2") # 40 matches
global_parity <- bind_rows(global_parity, NPL2_parity)

# National PUBG League: Contenders - Phase 1
# https://liquipedia.net/pubg/National_PUBG_League/2019/Contenders/Phase_1
NPLC1_parity <- tibble(points = c(133, 133, 122, 108, 
                                   106, 99, 96, 92, 
                                   89, 87, 76, 74, 
                                   67, 61, 48), # one team disqualified
                 phase = "NPLC1") # 32 matches
global_parity <- bind_rows(global_parity, NPLC1_parity)

# National PUBG League: Contenders - Phase 2
# https://liquipedia.net/pubg/National_PUBG_League/2019/Contenders/Phase_2
NPLC2_parity <- tibble(points = c(200, 125, 106, 103, 
                                    98, 96, 90, 83, 
                                    82, 81, 80, 73, 
                                    71, 53, 50, 42),
                         phase = "NPLC2") # 32 matches
global_parity <- bind_rows(global_parity, NPLC2_parity)

# PUBG Europe League: Phase 2
# https://liquipedia.net/pubg/PUBG_Europe_League/2019/Phase_2
PEL2_parity <- tibble(points = c(705, 690, 686, 682,
                                 568, 563, 531, 531,
                                 518, 499, 498, 495,
                                 478, 442, 429, 391),
                         phase = "PEL2") # 96 matches
global_parity <- bind_rows(global_parity, PEL2_parity)

# PUBG Europe League: Contenders - Phase 2
# https://liquipedia.net/pubg/PUBG_Contenders_League/2019/Phase_2
PELC2_parity <- tibble(points = c(356, 341, 335, 321, 
                                  305, 303, 302, 279, 
                                  268, 262, 238, 230, 
                                  219, 213, 207, 166),
                         phase = "PELC2") # just finals, not group stage
# unclear how many matches in finals
global_parity <- bind_rows(global_parity, PELC2_parity)

global_parity <- dplyr::mutate(global_parity, phase = factor(phase))

```

``` {r simpsons_index_viz, echo = FALSE, message = FALSE, results = "hide", fig.height = 6.5, fig.width = 8}

# plot for all leagues

# find inverse simpson's index for all teams
# boostrap estimates of 95% confidence interval upper and lower bounds for each index
# create dataframe with these values
compare_parity <- global_parity %>%
  group_by(phase) %>%
  summarise(invsimpson = diversity(points, index = "invsimpson"),
            lower_ci = H_boot(points, index = "invsimpson", R = 2000, ci = 95)$CI[1],
            upper_ci = H_boot(points, index = "invsimpson", R = 2000, ci = 95)$CI[2])

# create inverse simpson's index and CI plot
pp <- compare_parity %>%
  mutate(phase = fct_reorder(phase, invsimpson, .desc = FALSE)) %>%
  ggplot(aes(phase, invsimpson)) +
      geom_segment(aes(x = phase, 
                     y = lower_ci, 
                     xend = phase, 
                     yend = upper_ci,
                     color = phase)) +
      scale_color_viridis(discrete = TRUE,
                          option = "viridis", 
                          direction = 1, 
                          guide = FALSE,
                          begin = 0,
                          end = 1) +
      geom_point(color = "white", 
                 shape = 16, 
                 size = 4) +
      geom_point(color = "black", 
                 shape = 16, 
                 size = 1.3) +
      xlab("League and Phase") +
      ylab("Parity (Effective Number of Teams)") +
      theme_bw() +
      theme(axis.title.y = element_text(margin = margin(r = 20)), 
           axis.title.x = element_text(margin = margin(t = 10)),
           axis.text.x = element_blank(),
           axis.ticks.x = element_blank(), 
           panel.grid.major = element_line(color = "white"),
           text = element_text(family = "Helvetica Neue", size = 12))

pp <- pp + geom_text(aes(x = phase, 
                          y = lower_ci - 0.1,
                          label = phase,
                          family = "Helvetica"),
                      size = 2.5)

suppressWarnings(print(pp))

```

^*Figure 2: Parity in competitive PUBG. Inverse Simpson's indices, with confidence intervals, for each phase of every major international league with a 16-team lobby, showing the effective number of teams in each league. Numbers on the ends of league acronyms refer to the phase.*^

&#x200B;

**PEL Phase 2 had the highest parity of all major international PUBG leagues**, followed by PEL Contenders Phase 2, with a very dramatic jump in PEL-C parity from Phase 1.

This isn't necessarily what I expected to see based on the addition of two different teams to PEL Phase 2, but it's clear from the first plot that within the two clusters in the standings, teams are fairly close to each other on the whole.

**This might have interesting implications for the number of matches in future phases.** With the top four teams sitting comfortably at the top of the standings since basically the end of Week 2, was it really necessary to play 72 more matches to see which of those four teams, with near-equal points totals throughout, would happen to put together more good games in a row near the end?

On the other hand, without playing all 96 matches, Pittsburgh Knights wouldn't have had the opportunity to take over the 5^th^ place spot in the final weekend in such dramatic style. We'll see what Phase 3 looks like, I guess!

As always, my .Rmd file is [here](https://github.com/vecoris/PUBG_Dataviz/blob/master/2019-07-10-pel-phase-2-overview.Rmd), for those of you who are interested.

&#x200B;

**tl;dr Interactive tool to see how teams performed in PEL Phase 2. The top four teams (FaZe Clan, Natus Vincere, Team Liquid, and G2) separated out from the pack early on. A slow decline by Team SoloMid let the race for 5^th^ place be decided in just the final weekend with a great performance by Pittsburgh Knights. Also, PEL Phase 2 and PEL Contenders Phase 2 had the highest parity of all leagues so far.**